\textbf{Optimization of Porous Silicon Gradient Refractive Index Structures.}

### 2020-09-17 paper.tex
Finish rewriting paper

\documentclass{article}
\usepackage{amsmath}
\usepackage{graphicx} % gráficos
\usepackage[noblocks]{authblk}
%\usepackage{authblk}
%\usepackage[•]{•}ckage{float}
%\usepackage{cite}% para contraer referencias
%\usepackage[usenames]{color}
\usepackage{showkeys}
\usepackage{bm}
\usepackage{hyperref}
\usepackage[normalem]{ulem} %opcional para la correcciones
\newcommand{\abs}[1]{\lvert#1\rvert}
\usepackage{xcolor}
\newif{\ifinclude}
\newcommand{\notaL}[1]{{\color{blue}+L:#1+}}
\newcommand{\notaC}[1]{{\color{green}+C:#1+}}
\newcommand{\notaV}[1]{{\color{red}+V:#1+}}

@@

\section{Conclusions}
\label{sec:conclusion}
By choosing a simple geometry for our electrochemical cell, namely, a
rectangular prism, and employing a point-like electrode, we were able
to derive an expression for the calculation of the electric current
density along the surface of a Si sample. The expression was obtained
by using image charge theory and a planewise summation of Coulomb
potentials in 2D reciprocal space, and it is made up of
a rapidly converging sum of analytical terms. This allows the characterization
of the porosity of a PS layer and the etching
rate for different values of the etching current density by making
optical measurements on several positions of just a
few samples. We illustrated the procedure with two samples each of which we
measured at three different positions. These calibration curves are
very useful as the etching rate for the formation of porous silicon
and the resulting porosity is very sensitive to the growth conditions
and to the properties of the substrate, such as its doping. Thus,
there are no universal calibration curves. Having obtained these calibration curves
and being able to compute the current density at different positions
allows the prediction of the properties of GRIN structures. We
illustrated this by desigining a PS GRIN microcavity tuned at one
position to a given wavelength. We found a good agreement between its
measured reflectance spectra at different points with the spectra
calculated from the values of the expected local current
density using the calibration curves. We also found good agreement
between the measured and the expected geometry of the system. These
results show that the use of a simple electrolytic cell and our
computational procedure does allow the accurate prediction of the
optical properties of GRIN structures, and thus we believe it will
prove helpful for the design, fabrication, and characterization of novel
devices based on PS GRIN systems.

\section*{Acknowledgments}
\label{sec:acknowledgments}
WLM acknowledges the support of DGAPA-UNAM under grant IN111119.
% \backmatter
%\nocite{*}
%\bibliographystyle{plain}
%\bibliography{bibliografía.bib} %Aquí ponen el nombre del archivo .bib
\notaL{Manda toda la bibliografía a un archivo .bib}
\notaL{Cuando esté listo, quiero que me expliques por qué incluiste
  cada uno de los artículos citados}
\bibliographystyle{unsrt}
\begin{thebibliography}{XX}
  % forma de biblio es MLA
\bibitem{I1} P. Yeh,\textquotedblleft \emph{Optical Waves in Layered
    Media} \textquotedblright, 2nd edn. (Wiley-Interscience
  Publication,
  USA, 2005).
\bibitem{I2}Canham, L. 1997.\textquotedblleft \emph{Properties of
    Porous Silicon} \textquotedblright. Edited by Canham L. DERA,
  Malvern, UK.
\bibitem{I3}{Beale, M.I.J, J.D Benjamin, M.J Uren, N.G Chew, and A.G
    Cullis. 1985. \emph{ \textquotedblleft An Experimental and
      Theoretical Study of the Formation and Microstructure of
      Porous Silicon.\textquotedblright} J. Crystal Growth 73:
    622?36. doi:10.1021/jp0706984. }
\bibitem{I4}Canham, L. T. 1990. \emph{\textquotedblleft Silicon
    Quantum Wire Array Fabrication by Electrochemical and Chemical
    Dissolution of Wafers.\textquotedblright} Applied Physics
  Letters 57 (10): 1046. doi:10.1063/1.103561.
\bibitem{I5} J. D. Joannopoulos et al.,\textquotedblleft
  \emph{Photonic Crystals: Molding the Flow of
    Light}\textquotedblright, 2nd edn.
  (Princeton University Press, UK, 2008).
\bibitem{I6} E. Yablonovitch, \textquotedblleft \emph{Photonic
    band-gap structures,}\textquotedblright J. Opt. Soc. Am. B 10,
  283-295 (1993)
\bibitem{I7} Ilyas, S., and M. Gal.  \textquotedblleft \emph{
    Optical devices from porous silicon having continuously varying
    refractive index.}\textquotedblright Journal of Materials
  Science: Materials in Electronics 18.1 (2007): 61-64.
\bibitem{I8} Tran, P. \textquotedblleft \emph{Optical switching with
    a nonlinear photonic crystal: a numerical
    study.}\textquotedblright Optics letters 21.15 (1996):
  1138-1140.
\bibitem{I9} Ariza-Flores, A. David, L. M. Gaggero-Sager, and
  V. Agarwal. \textquotedblleft \emph{White metal-like
    omnidirectional mirror from porous silicon dielectric
    multilayers.}\textquotedblright Applied Physics Letters 101.3
  (2012): 031119.
\bibitem{I10} Johnson, Steven G., et al.  \textquotedblleft
  \emph{Linear waveguides in photonic-crystal
    slabs.}\textquotedblright Physical Review B 62.12 (2000): 8212.

>>>>

\documentclass{article}
\usepackage{amsmath}
\usepackage{graphicx} % gráficos
\usepackage[noblocks]{authblk}
%\usepackage{authblk}
%\usepackage[•]{•}ckage{float}
%\usepackage{cite}% para contraer referencias
%\usepackage[usenames]{color}
%\usepackage{showkeys}
\usepackage{bm}
\usepackage{hyperref}
\usepackage[normalem]{ulem} %opcional para la correcciones
\newcommand{\abs}[1]{\lvert#1\rvert}
\usepackage{xcolor}
\newif{\ifinclude}
\newcommand{\notaL}[1]{{\color{blue}+L:#1+}}
\newcommand{\notaC}[1]{{\color{green}+C:#1+}}
\newcommand{\notaV}[1]{{\color{red}+V:#1+}}

@@

\section{Conclusions}
\label{sec:conclusion}
By choosing a simple geometry for our electrochemical cell, namely, a
rectangular prism, and employing a point-like electrode, we were able
to derive an expression for the calculation of the electric current
density along the surface of a Si sample. The expression was obtained
by using image charge theory and a planewise summation of Coulomb
potentials in 2D reciprocal space, and it is made up of
a rapidly converging sum of analytical terms, just a few of which
should be kept. This allows the characterization
of the porosity of a PS layer and the etching
rate for different values of the etching current density by making
optical measurements on several positions of just a
few samples. We illustrated the procedure with three samples on each of which we
measured reflectance spectra at eight different positions.
Through a optimization procedure we fitted the porosity and etching
rate corresponding to each current density.
We showed that an analysis of the data of just one of the samples, which we chose
as that with the largest current density range, yielded calibration
curves that allow the approximate prediction of the properties of the other
samples. The calibration curves can be used to design and calculate the optical
properties of other systems prepared under similar conditions, such as
multilayered GRIN systems from which photonic crystals, microcavities
and sensors with position dependent properties. This is the subject of
ongoing work. As the etching rate for the formation of porous silicon
and the resulting porosity are very sensitive to the growth conditions
and to the properties of the substrate, such as its doping,
there are no universal calibration curves. Thus, it is useful to have
a procedure that from just one sample can produce calibration curves
that may be employed for other samples grown in the same conditions.

\section*{Acknowledgments}
\label{sec:acknowledgments}
WLM acknowledges the support of DGAPA-UNAM under grant
IN111119. \notaL{Cristian debe agradecer a conacyt y faltan
  agradecimientos de Vivechna (quizás incluyendo al icf)}
% \backmatter
%\nocite{*}
%\bibliographystyle{plain}
%\bibliography{bibliografía.bib} %Aquí ponen el nombre del archivo .bib
\notaL{Manda toda la bibliografía a un archivo .bib}
\notaL{Cuando esté listo, quiero que me expliques por qué incluiste
  cada uno de los artículos citados}
\bibliographystyle{unsrt}
\begin{thebibliography}{XX}
  % forma de biblio es MLA
\bibitem{I1} P. Yeh,\textquotedblleft \emph{Optical Waves in Layered
    Media} \textquotedblright, 2nd edn. (Wiley-Interscience
  Publication,
  USA, 2005).
\bibitem{I2}Canham, L. 1997.\textquotedblleft \emph{Properties of
    Porous Silicon} \textquotedblright. Edited by Canham L. DERA,
  Malvern, UK.
\bibitem{I3}{Beale, M.I.J, J.D Benjamin, M.J Uren, N.G Chew, and A.G
    Cullis. 1985. \emph{ \textquotedblleft An Experimental and
      Theoretical Study of the Formation and Microstructure of
      Porous Silicon.\textquotedblright} J. Crystal Growth 73:
    622?36. doi:10.1021/jp0706984. }
\bibitem{I4}Canham, L. T. 1990. \emph{\textquotedblleft Silicon
    Quantum Wire Array Fabrication by Electrochemical and Chemical
    Dissolution of Wafers.\textquotedblright} Applied Physics
  Letters 57 (10): 1046. doi:10.1063/1.103561.
\bibitem{I5} J. D. Joannopoulos et al.,\textquotedblleft
  \emph{Photonic Crystals: Molding the Flow of
    Light}\textquotedblright, 2nd edn.
  (Princeton University Press, UK, 2008).
\bibitem{I6} E. Yablonovitch, \textquotedblleft \emph{Photonic
    band-gap structures,}\textquotedblright J. Opt. Soc. Am. B 10,
  283-295 (1993)
\bibitem{I7} Ilyas, S., and M. Gal.  \textquotedblleft \emph{
    Optical devices from porous silicon having continuously varying
    refractive index.}\textquotedblright Journal of Materials
  Science: Materials in Electronics 18.1 (2007): 61-64.
\bibitem{I8} Tran, P. \textquotedblleft \emph{Optical switching with
    a nonlinear photonic crystal: a numerical
    study.}\textquotedblright Optics letters 21.15 (1996):
  1138-1140.
\bibitem{I9} Ariza-Flores, A. David, L. M. Gaggero-Sager, and
  V. Agarwal. \textquotedblleft \emph{White metal-like
    omnidirectional mirror from porous silicon dielectric
    multilayers.}\textquotedblright Applied Physics Letters 101.3
  (2012): 031119.
\bibitem{I10} Johnson, Steven G., et al.  \textquotedblleft
  \emph{Linear waveguides in photonic-crystal
    slabs.}\textquotedblright Physical Review B 62.12 (2000): 8212.
